\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{tikz}
\usepackage{fancyhdr,xcolor}
\usepackage{mathptmx}
\usepackage{anyfontsize}
\usepackage{t1enc}
\usepackage{fontspec}
\usepackage{hyperref}
\usepackage[absolute,overlay]{textpos}
\usepackage[left=-5cm, top=-1cm, right=5cm]{geometry}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{lipsum}
\mdfdefinestyle{Frame1}{%
    linecolor=black,
    outerlinewidth=1pt,
    roundcorner=10pt,
    innertopmargin=10pt,
    innerbottommargin=10pt,
    innerrightmargin=5pt,
    innerleftmargin=10pt,
    backgroundcolor=black}
    
\setmainfont{Nunito}[
  Path=./,
  Extension=.ttf,
  UprightFont=*-Light,
  BoldFont=*-Bold,
]
\pagenumbering{gobble}
\pagestyle{fancy}
\begin{document}
\begin{tikzpicture}
\draw  [fill=black] (-10,-10) rectangle ++(30,5);
\end{tikzpicture}
\begin{center}
\begin{textblock*}{10cm}(5.5cm,1.2cm)
   \textcolor{white}{\fontsize{30}{40}\selectfont Yash Karande}
\end{textblock*}
\begin{textblock*}{10cm}(5.5cm,2.4cm)
\textcolor{white}{\fontsize{12}{15}\selectfont \href {mailto:kyashkarande@gmail.com} {kyashkarande@gmail.com} | +91-8668230701}
\end{textblock*}
\end{center}
\begin{tikzpicture}
\draw  [black] rectangle ++(0,30);
\end{tikzpicture}
\begin{textblock*}{3.9cm}(1cm,5.0cm)
   \begin{mdframed}[style=Frame1]
   \textcolor{white}{\fontsize{20}{20}\selectfont Summary }
   \end{mdframed}
\end{textblock*}
\begin{textblock*}{14cm}(6.5cm,5.0cm)
   \textcolor{black}{\fontsize{15}{20}\selectfont A hardworking, dedicated and highly motivated student looking for a responsible career opportunity at your organization, where I can utilize my training, programming and management skills, human resource, while making a significant contribution to the success of the organization.}
\end{textblock*}
\begin{textblock*}{4cm}(1cm,9.0cm)
   \begin{mdframed}[style=Frame1]
   \textcolor{white}{\fontsize{20}{20}\selectfont Education}
   \end{mdframed}
\end{textblock*}
\begin{textblock*}{14cm}(6.5cm,9.0cm)
   \textcolor{black}{\fontsize{15}{20}\selectfont \underline{\textbf{BE, Computer Engineering (SPPU)} \hspace{25mm}\textbf{(2016-2020)}}\vspace{1mm} \newline{Sandip Institute of Technology\\ and Research Center, Nashik. \hspace{15mm}\textbf{ CGPA: 7.80 / 68.64\% }}}
\end{textblock*}
\begin{textblock*}{14cm}(6.5cm,11.6cm)
   \textcolor{black}{\fontsize{15}{20}\selectfont \underline{\textbf{HSC, Science (Maharashtra Board)\hspace{25mm} (2014-2016)}}\vspace{2mm} \newline{KTHM, Nashik \hspace{85mm}  \textbf{74.77\%.}}}
\end{textblock*}
\begin{textblock*}{14cm}(6.5cm,13.6cm)
   \textcolor{black}{\fontsize{15}{20}\selectfont \underline{\textbf{SSC (Maharashtra Board) \hspace{6cm} (2014)}}\vspace{2mm} \newline{GGSPS, Nashik \hspace{80mm}  \textbf{86.60\%.}}}
\end{textblock*}
\begin{textblock*}{3.5cm}(1cm,16cm)
   \begin{mdframed}[style=Frame1]
   \textcolor{white}{\fontsize{20}{20}\selectfont Projects}
   \end{mdframed}
\end{textblock*}
\begin{textblock*}{14cm}(6.5cm,16cm)
\begin{enumerate}
    \item \textcolor{black}{\fontsize{14}{20}\selectfont \textbf{Internal Job Posting:} A pure REST API project built with Slim, PHP and PostgreSQL for internal hiring of employees in an organisation.}
    \item \textcolor{black}{\fontsize{14}{20}\selectfont \textbf{Kitchen dashboard:} Made to automate daily tasks required in mess services. Written in Angular with Firebase as database and used firebase functions for crons.}
    \item \textcolor{black}{\fontsize{14}{20}\selectfont \textbf{Secured e-Assessment using blockchain:} Main objective was to eradicate the flaws in examination systems that use traditional database systems with the use of blockchain. Made with Hyperledger fabric, Angular and Node.js.}
    \item \textcolor{black}{\fontsize{14}{20}\selectfont \textbf{To-Do app:} Made for Hackerearth's StackHack 1.0, which consists of frontend made in Angular and backend with Node.js with MongoDB as database.}
    \item \textcolor{black}{\fontsize{14}{20}\selectfont \textbf{Event management dashboard:} A client side application written in angular for management of guests, speakers, audience, etc.}
    \item \textcolor{black}{\fontsize{14}{20}\selectfont \textbf{CSV to Table:} Client side application which imports CSV and displays it in tabular format also providing the user to sort, search \& merge data.}
    \item \textcolor{black}{\fontsize{14}{20}\selectfont \textbf{Image classifier:} An image classifier made using python and tensorflow.}
\end{enumerate}
\end{textblock*}
\newpage
\begin{textblock*}{2.5cm}(1cm,2.00cm)
   \begin{mdframed}[style=Frame1]
   \textcolor{white}{\fontsize{20}{20}\selectfont Skills}
   \end{mdframed}
\end{textblock*}
\begin{textblock*}{14cm}(6.5cm,2.00cm)
\begin{enumerate}
    \item \textcolor{black}{\fontsize{14}{20} \selectfont \textbf{Frameworks/technologies:} Angular, Slim, Node.js, Flutter.}
    \item \textcolor{black}{\fontsize{14}{20} \selectfont \textbf{Programming languages:} Typescript, PHP, C++, Java, Python}
    \item \textcolor{black}{\fontsize{14}{20} \selectfont \textbf{Databases:} Firebase, PostgreSQL, MongoDB.}
    \item \textcolor{black}{\fontsize{14}{20} \selectfont \textbf{Others:} Git, Bash.}
\end{enumerate}
\end{textblock*}
\begin{tikzpicture}
\draw  [white] (-10,-10) rectangle ++(30,5);
\end{tikzpicture}
\begin{tikzpicture}
\draw  [fill=black] rectangle ++(0,30);
\end{tikzpicture}
\begin{textblock*}{3.50cm}(1cm,7.00cm)
   \begin{mdframed}[style=Frame1]
   \textcolor{white}{\fontsize{20}{20}\selectfont Courses}
   \end{mdframed}
\end{textblock*}
\begin{textblock*}{14cm}(6.5cm,7.00cm)
\begin{enumerate}
    \item \textcolor{black} {\fontsize{14}{20}\selectfont \textbf{\href{https://drive.google.com/drive/folders/1vIvJdWDVqlOQucVfQsaUvrnagXEP9WfX}{Machine Learning}} - Andrew Ng (Coursera) }
    \item \textcolor{black} {\fontsize{14}{20}\selectfont \textbf{Flutter and Dart - The Complete Guide} - Maximilian Schwarzmüller (Udemy)}
    \item \textcolor{black} {\fontsize{14}{20}\selectfont \textbf{\href{https://drive.google.com/drive/folders/1iNJ9KclRptNXeT2hnjGS4JAHuWdt_E-u}{Blockchain Basics}} - Bina Ramamurthy (Coursera) }
\end{enumerate}
\end{textblock*}
\begin{textblock*}{3.6cm}(1cm,11.00cm)
   \begin{mdframed}[style=Frame1]
   \textcolor{white}{\fontsize{20}{20}\selectfont Hobbies/\\Interests}
   \end{mdframed}
\end{textblock*}
\begin{textblock*}{14cm}(6.5cm,11.00cm)
\begin{enumerate}
    \item \textcolor{black}{\fontsize{14}{20}\selectfont Maintaining and building custom\vspace{1mm} roms and kernels for android devices.}
    \item \textcolor{black}{\fontsize{14}{20}\selectfont Making UI/UX designs on Adobe XD and Figma.}
    \item \textcolor{black}{\fontsize{14}{20}\selectfont Creating various other content like illustrations and cinematic \vspace{1mm} videos.}
\end{enumerate}
\end{textblock*}
\end{document}